
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 14: Twitters Mining with rtweet"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment14.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


[Sample Codes](https://bryantstats.github.io/math421/slides/16_text_mining_rtweet.html)

-------


```{r}
library(rtweet) 
library(tidytext)
library(ggplot2)
library(ggpubr)
library(tidyverse) 
library(knitr)
library(lubridate)
```


1. Pick a keyword or hashtag. Download the data associated with the keyword/hashtag. Plot at least 5 plots to visualize the data associated with the keyword/hashtag. All plots should have titles and captions.

```{r}
auth_setup_default()

keyword_search = '#steelers'

df <- search_tweets(q = keyword_search, 
                        n = Inf, # number of tweets
                        include_rts = FALSE,
                        `-filter` = "replies",
                        lang = "en") %>% 
  mutate(created_at = ymd_hms(format(created_at, tz = "US/Eastern")))

write_csv(df, 'twitter_data.csv')
```

```{r}
df <- read_csv('twitter_data.csv')
```

```{r}
ts_plot(df, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets by time",
       subtitle = paste0(format(min(df$created_at), "%d %B %Y"), " to ", format(max(df$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") +
  theme_minimal()
```

```{r}
df %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10)
```

```{r}
df %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10) %>% 
  ggplot(aes(x = n, y = reorder(mentions, n)))+
  geom_col()+
  labs(x = 'Top 10 mentions in the tweets', y = '')
```

```{r}
df %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#steelers",'#pittsburgh','#pittsburghsteelers','#nfl'), str_detect(hashtag, "^#")) %>% 
  count(hashtag, sort = TRUE) %>%
  head(20)
#filter(created_at>='2022-11-14') %>% 
```

```{r}
df %>% 
  filter(created_at>='2022-11-14') %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#steelers",'#pittsburgh','#pittsburghsteelers','#nfl'), str_detect(hashtag, "^#")) %>% 
  count(hashtag, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(hashtag, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```

```{r}
library(RColorBrewer)

pal <- brewer.pal(8,"Dark2")
library(wordcloud) 

df %>% 
  filter(created_at>='2022-11-14') %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#steelers",'#pittsburgh','#pittsburghsteelers','#nfl'), str_detect(hashtag, "^#")) %>% 
  count(hashtag, sort = TRUE) %>%
  mutate(hashtag = str_remove(hashtag, '#')) %>% 
  filter(hashtag != 'nfl') %>% 
  with(wordcloud(hashtag, n, random.order = FALSE, max.words = 50, colors = pal))
```

```{r}
#Install emo pakage:
devtools::install_github("hadley/emo")

library(emo)
df %>%
  mutate(emoji = ji_extract_all(text)) %>%
  unnest(cols = c(emoji)) %>%
  count(emoji, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(y=reorder(emoji,n), x=n)) +
  geom_col()+
  theme(axis.text.y = element_text(size = 40))+
  labs(x = 'Top Emoji in the tweets', y = '')
```


2. Choose a location then pick a trending keyword/hashtag in the location. Download the data associated with the keyword/hashtag. Plot at least 5 plots to visualize the data associated with the keyword/hashtag. All plots should have titles and captions.

```{r}
trends_available()
```
```{r}
get_trends('Providence')
```

```{r}
auth_setup_default()

keyword_search = '#inouebutler'

df2 <- search_tweets(q = keyword_search, 
                        n = Inf, # number of tweets
                        include_rts = FALSE,
                        `-filter` = "replies",
                        lang = "en") %>% 
  mutate(created_at = ymd_hms(format(created_at, tz = "US/Eastern")))

write_csv(df2, 'twitter_data_InoueButler.csv')
```

```{r}
df2 <- read_csv('twitter_data_InoueButler.csv')
```

```{r}
ts_plot(df2, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets by time",
       subtitle = paste0(format(min(df2$created_at), "%d %B %Y"), " to ", format(max(df2$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") +
  theme_minimal()
```

```{r}
df2 %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10) %>% 
  ggplot(aes(x = n, y = reorder(mentions, n)))+
  geom_col()+
  labs(x = 'Top 10 mentions in the tweets', y = '')
```

```{r}
df2 %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  count(hashtag, sort = TRUE) %>%
  head(20)
```
```{r}
df2 %>% 
  filter(created_at>='2022-11-14') %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  count(hashtag, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(hashtag, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '')
```

```{r}
library(RColorBrewer)

pal <- brewer.pal(8,"Dark2")
library(wordcloud) 

df2 %>% 
  filter(created_at>='2022-11-14') %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  count(hashtag, sort = TRUE) %>%
  mutate(hashtag = str_remove(hashtag, '#')) %>% 
  with(wordcloud(hashtag, n, random.order = FALSE, max.words = 50, colors = pal))
```

```{r}
devtools::install_github("hadley/emo")

library(emo)
df2 %>%
  mutate(emoji = ji_extract_all(text)) %>%
  unnest(cols = c(emoji)) %>%
  count(emoji, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(y=reorder(emoji,n), x=n)) +
  geom_col()+
  theme(axis.text.y = element_text(size = 40))+
  labs(x = 'Top Emoji in the tweets', y = '')
```

