
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 11: Predictive Modeling - Universal Framework"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment11.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


-------

1. Install the package mlbench and use the follows to import the data

```{r}
library(mlbench)
library(tidyverse)
data(PimaIndiansDiabetes)
df <- tibble(PimaIndiansDiabetes)
```

Train and Test a decision tree and a random forest with caret. Plot the variable importance of these models.

```{r}
library(caret)

df <- df %>%
  mutate(diabetes = as.factor(diabetes))
splitIndex <- createDataPartition(df$diabetes, p = .90, list = FALSE)

df_train <- df[splitIndex,]
df_test <- df[-splitIndex,]
```

```{r}
tree <- train(diabetes ~ ., data=df_train, method = "rpart2", maxdepth=3)

prediction1 <- predict(tree, df_test)
confmatrix1 <- confusionMatrix(data = prediction1, reference = df_test$diabetes)
confmatrix1$overall[1]
```
```{r}
forest <- train(diabetes~., data=df_train, 
                method = "rf",
                ntree = 1000) 
prediction2 <- predict(forest, df_test)
confmartrix2 <- confusionMatrix(data = prediction2, reference = df_test$diabetes)
confmartrix2$overall[1]
```

```{r}
plot(varImp(tree))
```

```{r}
plot(varImp(forest))
```

2. Train and Test a `glmnet` model. Plot the variable importance of the model.

```{r}
library(glmnet)
glmModel <- train(diabetes ~ ., data=df_train, 
                method = "glmnet")
prediction3 <- predict(glmModel, df_test)
confmatrix3 <- confusionMatrix(data = prediction3, reference = df_test$diabetes)
confmatrix3$overall[1]
```

```{r}
plot(varImp(forest))
```

3. Train and test two models that are not `ranger`, `glmnet` or `rpart`  with caret. If possible, plot the variable importance of the model.

```{r}
model3_1 <- train(diabetes ~ ., data=df_train, method = "rpart1SE")
prediction3_1 <- predict(model3_1, df_test)
confmatrix3_1 <- confusionMatrix(data = prediction3_1, reference = df_test$diabetes)
confmatrix3_1$overall[1]
```

```{r}
plot(varImp(model3_1))
```

```{r}
model3_2 <- train(diabetes ~ ., data=df_train, method = "rpart2")
prediction3_2 <- predict(model3_2, df_test)
confmatrix3_2 <- confusionMatrix(data = prediction3_2, reference = df_test$diabetes)
confmatrix3_2$overall[1]
```

```{r}
plot(varImp(model3_2))
```

