
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment8.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install two packages `gganimate` and `gifski` then restart Rstudio. Using the `Adult Census Income` data, make an animation using `geom_point` and `transition_states`.
```{r,eval=FALSE}
install.packages('gganimate')
install.packages('gifski')
```
```{r}
df <- read.csv('adult_census_missing.csv')
names(df)
```


```{r}
library(gganimate)
library(gifski)
library(ggplot2)
library(dplyr)
library(tidyverse)

df <- df %>%
  na_if("Not known") %>%
  na_if("?") %>%
  na_if("Unknown")

df <- drop_na(df)
```

```{r}
g <- ggplot(df, aes(x = hours.per.week, y = capital.gain))+
  geom_point() + 
  transition_states(sex)+
  labs(title ='{closest_state}')
animate(g)
```

2. Using the `Adult Census Income` data, make an animation using `geom_bar` and `transition_states`.
```{r}
g <- ggplot(df, aes(x = workclass))+
  geom_bar() + 
  transition_states(sex)+
  labs(title ='{closest_state}')
animate(g)
```

3. Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19 in 2021.

```{r}
library(lubridate)
library(knitr)

df3 <- read.csv('WHO-COVID-19-global-data.csv')
```

```{r}
df3$week <- week(df3$Date_reported)
df3 <- df3 %>% 
  group_by(week, Country) %>%
  summarise(mean = mean(New_cases)) %>%
  group_by(week) %>% mutate(rank=rank(-mean)) %>%
  filter(rank <= 10) %>%
  ggplot(aes(x=rank, y=mean, group=Country, fill=Country, label=Country)) +
  geom_col()+
  geom_text(aes(y = mean, label = Country), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Week {closest_state}', x='', y='Number of Positive Cases', fill='Country')+
    theme(plot.title = element_text(hjust = 1, size = 22), axis.ticks.y = element_blank(), axis.text.y  = element_blank()) + 
    transition_states(week)+
    ease_aes("cubic-in-out")
animate(df3, nframes = 1000)
```


4. Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (https://covidtracking.com/data/download/all-states-history.csv) but you should make a different bar racev from ones in the slides. 

```{r}
df4 <- read.csv('all-states-history.csv')
names(df4)
```

```{r}
library(lubridate)
library(knitr)

df4$week <- week(df4$date)
df4 <- df4 %>% 
  group_by(week, state) %>%
  summarise(mean = mean(positive)) %>%
  group_by(week) %>% mutate(rank=rank(-mean)) %>%
  filter(rank <= 10) %>%
  ggplot(aes(x=rank, y=mean, group=state, fill=state, label=state)) +
  geom_col()+
  geom_text(aes(y = mean, label = state), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Week {closest_state}', x='', y='Number of Positive Cases', fill='State')+
    theme(plot.title = element_text(hjust = 1, size = 22), axis.ticks.y = element_blank(), axis.text.y  = element_blank()) + 
    transition_states(week)+
    ease_aes("cubic-in-out")
animate(df3, nframes = 1000)
```


