
---
title: "Final Question 2"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: logo.png
    source_code: embed
    social: menu
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(knitr)
library(DT)
df <- read_csv('ScoobyDoo.csv')
```

{.sidebar}
=======================================================================

### 1. Scooby-Doo

Every Scooby-Doo episode and movie's various variables.

Took ~1 year to watch every Scooby-Doo iteration and track every variable. Many values are subjective by nature of watching but I tried my hardest to keep the data collection consistent.

### 2. Flexdashboard and Plotly

This interactive uses `flexdashboard` and `plotly` to visualize the data. 

Dataset
=======================================================================

### The Dataset

```{r}
datatable(df, options = list(
  pageLength = 25
))
```


Plots
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

#### Plot 1

```{r}
q2p1 <- df %>%
  group_by(format) %>%
  ggplot()+ 
  geom_bar(mapping=aes(x=format, fill=arrested))+
  labs(x='Format', y='Count', fill='arrested')
ggplotly(q2p1)
```

#### Plot 2

```{r, include=FALSE}
dfq2p2 <- df %>%
  na_if("NULL") %>%
  drop_na(imdb)
```

```{r}
q2p2 <- dfq2p2 %>%
  ggplot()+ 
  geom_point(mapping=aes(x=index, y=imdb, color=network))+
  labs(x='Order Aired', y='IMDB Rating',color='network')
ggplotly(q2p2)
```

#### Plot 3

```{r}
q2p3 <- df %>%
  ggplot()+
  geom_histogram(mapping=aes(x=zoinks),bins=27)+
  labs(x="Zoinks Count")
ggplotly(q2p3)
```


#### Plot 4

```{r}
q2p4 <- df %>%
  ggplot()+
  geom_point(mapping = aes(x = index, y = engagement))+
  facet_wrap(~settingTerrain)+
  labs(x="Order Released",y="Engagement")
ggplotly(q2p4)
```


Column {data-width=500}
-----------------------------------------------------------------------

Column {data-width=500}
-----------------------------------------------------------------------

Example Text
=======================================================================

This third tab just has some example text.